---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lfe2fixest

<!-- badges: start -->
<!-- badges: end -->

The goal of **lfe2fixest** is to take R scripts that rely on the `felm()` function 
from the [**lfe**](https://github.com/sgaure/lfe) package and convert 
them to their `feols()` equivalents from the 
[**fixest**](https://github.com/lrberge/fixest) package.

Why would you want to do this?

Both `lfe::felm()` and `fixest::feols()` provide "fixed-effects" estimation 
routines for high-dimensional data. Both methods are also highly optimised. 
However, `feols()` is newer, tends to be significantly faster, and allows for 
additional functionality (e.g. a `predict` method). At the time writing this 
conversion package, **lfe** has also been (temporarily) removed from CRAN after
a period of stasis, leading to downstream issues.

The syntax between `lfe::felm()` and `fixest::feols()` is similar, if not quite 
offering a drop-in replacement. This package therefore aims to automate the 
conversion process; ignoring non-relevant arguments and differing options 
between the two, while doing its best to ensure that the resulting scripts will 
produce the same output.

## Installation

Install the package from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("grantmcdermott/lfe2fixest")
```
## Example

Start by loading the package.

```{r libs}
library(lfe2fixest)
```


Let's create a **lfe**-based R script, that's deliberately messy (inconsistent
formatting, etc.)

```{r lfe_script}
lfe_string = "
library(lfe)
library(modelsummary)

## Our toy dataset
aq = airquality
names(aq) = c('y', 'x1', 'x2', 'x3', 'mnth', 'dy')

## Simple OLS (no FEs)
mod1 = felm(y ~ x1 + x2, aq)

## Add a FE and cluster variable
mod2 = felm(y ~ x1 + x2 |
              dy |
              0 |
              mnth, aq)

## Add a second cluster variable and some estimation options
mod3 = felm(y ~ x1 + x2 |
              dy |
              0 |
              dy + mnth,
            cmethod = 'reghdfe', ## Also the same as feols
            exactDOF = TRUE,     ## Irrelevant option for feols (should be ignored)
            aq)

## IV reg with weights
mod4 = felm(y ~ 1 |
              dy |
              (x1 ~ x3) |
              mnth,
            weights = aq$x2,
            data = aq
            )

## Regression table
mods = list(mod1, mod2, mod3, mod4)
msummary(mods, gof_omit = 'Pseudo|Within|Log|IC', output = 'markdown')
"
writeLines(lfe_string, 'lfe_script.R')
```

We can now convert this script to the **fixest** equivalent using the package's
main function, `lfe2fixest()` (or its alias, `felm2feols()`). 

While the function accepts several arguments, the most important (and only
required) one is an input file. Similarly, if no output file argument is 
provided, then it will just print the conversion results to screen.

```{r fixest_script1}
lfe2fixest('lfe_script.R')
```

Looks good. Note that the `feols` (`felm`) model syntax has been cleaned up, 
with comments removed and everything collapsed onto a single line. Let's write 
it to disk by supplying an output file this time.

```{r fixest_script2}
lfe2fixest(infile = 'lfe_script.R', outfile = 'fixest_script.R')
```

Note that the `lfe2fixest()` is a pure conversion function. It never actually
runs anything from either the input or output files. That being, said here's a 
quick comparison of the resulting regressions &mdash; i.e. what we get if we 
actually *do* run the scripts. As an aside, my scripts make use of the excellent 
[**modelsummary**](https://vincentarelbundock.github.io/modelsummary/index.html) 
package to generate the simple regression tables that you see below, although 
we're really not showing off its functionality here.

First, the original **lfe** version:

```{r comparison, message  = FALSE}
source('lfe_script.R', print.eval = TRUE)
```

Second, the **fixest** conversion:

```{r comparison2, message  = FALSE}
source('fixest_script.R', print.eval = TRUE)
```

Some minor formatting differences aside, looks like it worked and we get the
exact same results from both scripts. Great!

Let's clean up before continuing.

```{r cleanup}
file.remove(c('lfe_script.R', 'fixest_script.R'))
```

## Caveats

This package was thrown together pretty quickly. Current limitations include:

- `feols()` offers a variety of optimised features and syntax for things like 
[varying slopes](https://cran.r-project.org/web/packages/fixest/vignettes/fixest_walkthrough.html#31_Varying_slopes), 
[multiple estimation](https://cran.r-project.org/web/packages/fixest/vignettes/multiple_estimations.html), 
etc. that go beyond the standard R syntax (although the latter still works. 
**lfe2fixest** doesn't try to exploit any of these specialised features. It's 
more or less a literal translation of the `felm()` formula. The goal is to get 
you up and running with as little pain as possible, rather than eking every 
extra bit out of `feols()`'s already amazing performance.
- We assume that users always provide a dataset in their model calls (i.e. 
regressions with global variables are not supported). 
- Similarly, the package only supports models that are explicitly written out in 
a script. If your models are constructed programatically (e.g. with `Formula()`) 
then the conversion probably won't work.
- Multiple IV regressions (i.e. multiple endogenous variables) are not yet 
supported.

I'll try to address these as time allows. PRs are most welcome.
