---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lfe2fixest

<!-- badges: start -->
<!-- badges: end -->

The goal of **lfe2fixest** is to take R scripts that rely on the `felm()` function 
from the [**lfe**](https://github.com/sgaure/lfe) package and convert 
them to their `feols()` equivalents from the 
[**fixest**](https://github.com/lrberge/fixest) package.

## Installation

Install the package from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("grantmcdermott/lfe2fixest")
```
## Example

Start by loading the package.

```{r libs}
library(lfe2fixest)
```


Let's create a **lfe**-based R script, that's deliberately messy (inconsistent
formatting, etc.)

```{r lfe_script}
lfe_string = "
library(lfe)
library(modelsummary)

## Our toy dataset
aq = airquality
names(aq) = c('y', 'x1', 'x2', 'x3', 'mnth', 'dy')

## Simple OLS (no FEs)
mod1 = felm(y ~ x1 + x2, aq)

## Add a FE and cluster variable
mod2 = felm(y ~ x1 + x2 |
              dy |
              0 |
              mnth, aq)

## Add a second cluster variable and some estimation options
mod3 = felm(y ~ x1 + x2 |
              dy |
              0 |
              dy + mnth,
            cmethod = 'reghdfe',
            exactDOF = TRUE,
            aq)

## IV reg with weights
mod4 = felm(y ~ 1 |
              dy |
              (x1 ~ x3) |
              mnth,
            weights = aq$x2,
            data = aq
            )

## Regression table
mods = list(mod1, mod2, mod3, mod4)
msummary(mods, gof_omit = 'Pseudo|Within|Log|IC', output = 'markdown')
"
writeLines(lfe_string, 'lfe_script.R')
```

We can convert it to something that is **fixest**-friendly using the package's
main (only!) function, `lfe2fixest::lfe2fixest()`. 

While the function accepts several arguments, the most important (and only
required) one is an input file. Similarly, if no output file argument is 
provided, then it will just print the conversion results to screen.

```{r fixest_script1}
lfe2fixest('lfe_script.R')
```

Looks good, let's write it to disk by supplying an output file this time.

```{r fixest_script2}
lfe2fixest(infile = 'lfe_script.R', outfile = 'fixest_script.R')
```

Note that the `lfe2fixest()` is a pure conversion function. It never actually
runs anything from either the input or output files. That being, said here's a 
quick comparison of the resulting regressions &mdash; i.e. what we get if we 
actually *do* run the scripts. Note that my scripts make use of the excellent 
[**modelsummary**](https://vincentarelbundock.github.io/modelsummary/index.html) 
package to generate the simple regression tables that you see below, although 
we're really (really) not showing off its functionality here.

First the lfe version:

```{r comparison, message  = FALSE}
source('lfe_script.R', print.eval = TRUE)
```

Then the fixest conversion:

```{r comparison2, message  = FALSE}
source('fixest_script.R', print.eval = TRUE)
```

Some minor formatting differences aside, looks like it worked and we get the
exact same results from both scripts. Great!

Let's clean up before continuing.

```{r cleanup}
file.remove(c('lfe_script.R', 'fixest_script.R'))
```

## Caveats

This package was thrown together pretty quickly. Current limitations include:

- `lfe2fixest()` assumes that users provide a dataset in their model calls (i.e. 
regressions with global variables are not supported). 
- `lfe2fixest()` does not yet handle multiple IV regression. 
- Comments inside the original `felm()` model call are liable to mess things up. 
- It only supports models that are explicitly written out in the script. If
your models are constructed programatically (e.g. with `Formula()`) then it
probably won't work.

I'll try to address these as time allows. PRs are most welcome.
